### 2021-05-20 papers/thesis/full/ch2-spherical-harmonics/spherical-harmonics.tex
minor edit

In this chapter, we demonstrate how one can write the Spherical Harmonics as polynomials in $(x, y, z)$, and how the relationships between them can be used to obtain sparse \enquote{Jacobi operators} for multiplication by $x,y,z$. We demonstrate how these in turn lead to an algorithm for evaluating the Spherical Harmonics, and further an efficient algorithm for evaluating functions when expanded in the SH OP basis. The techniques used here are done so with the aim of applying them to other OP families of other domains (and we do so in later chapters). We will finally demonstrate a proof-of-concept via the examples of the heat equation and the linearised shallow water equations on the unit sphere.

>>>>

In this chapter, we demonstrate how one can write the Spherical Harmonics as polynomials in $(x, y, z)$, and how the relationships between them can be used to obtain sparse \enquote{Jacobi operators} for multiplication by $x,y,z$. We demonstrate how these in turn lead to an algorithm for evaluating the Spherical Harmonics, an efficient algorithm for evaluating functions when expanded in the SH OP basis, and sparse \enquote{banded-block-banded} differential operator matrices. The techniques used here are done so with the aim of applying them to other OP families of other domains (and we do so in later chapters). We will finally demonstrate a proof-of-concept via the examples of the heat equation and the linearised shallow water equations on the unit sphere.
